Comparing R packages for calculation of persistent homology

### 2020-02-20 tdabench-paper/tdabench.Rmd
shortened phrasing
removed unnecessary phrase

Benchmark data was collected twice - once on a local machine and once on a remote computing node, each of which featured 16 GB random access memory.
Both datasets were compared for consistency and are publicly available at the repository linked below.
Data from the remote computing node is visualized in this report.
The larger point clouds required more than 16 GB of RAM to calculate persistent homology using a subset of the libraries; attempts to compute results resulted in runtime errors, and the corresponding output is missing from the corresponding figures and tables.
Fully reproducible code for all numerical results and figures in this report can be found at https://github.com/eashwarsoma/TDA-benchmark.

@@

Computing persistent homology of a canonical torus grants quick insight into efficiency of each library (Figure \ref{fig:tor}).
Dionysus exhibits the longest average runtime, and, although Ripser and GUDHI have similar runtimes for smaller point clouds, as the number of points increases Ripser eventually has a significant lead.
Next, we compare performance of these three libraries with multiple canonical datasets to ensure that the noted pattern generalizes.

>>>>

Benchmark data was collected twice - once on a local machine and once on a remote computing node, each of which featured 16 GB random access memory.
Both datasets were compared for consistency and are publicly available at the repository linked below.
Data from the remote computing node is visualized in this report.
The larger point clouds required more than 16 GB of RAM to calculate persistent homology using a subset of the libraries; attempts to compute results resulted in runtime errors, and the corresponding output is missing from the corresponding figures and tables.
Fully reproducible code for all numerical results and figures can be found at https://github.com/eashwarsoma/TDA-benchmark.

@@

Computing persistent homology of a canonical torus grants quick insight into efficiency of each library (Figure \ref{fig:tor}).
Dionysus exhibits the longest average runtime, and, although Ripser and GUDHI have similar runtimes for smaller point clouds, as the number of points increases Ripser eventually has a significant lead.
Next, we compare library performance with multiple canonical datasets to ensure that the noted pattern generalizes.
